%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Config
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsthm,amsmath,amssymb,amsfonts}
\usepackage{xcolor}

% package for japanese text
\usepackage{CJKutf8}
% commands for japanese
\newcommand{\beginjapanese}{\begin{CJK}{UTF8}{ipxm}}
\newcommand{\finishjapanese}{\end{CJK}}

% Title page
\title{Instructions for Updating the Sendai Logic Homepage}
\author{Leonardo Vieira Pacheco Braga}

\begin{document}
\maketitle

sendailogic.com is currently generated using \texttt{hugo} (gohugo.io) and hosted using \texttt{github pages} (https://pages.github.com).
It can be accessed via sendailogic.com or sendailogic.github.io.
The github folder is at
\begin{quote}
    https://github.com/sendailogic/sendailogic.github.io.
\end{quote}

Note: this document assumes basic knowledge about using the command line of your operating system.
% Any tutorial should give you enough information in order to use it.

\section{Preparation}
These steps have to be done anytime you want to edit the site on a new computer.

\begin{itemize}
    \item Download GitHub Desktop at https://desktop.github.com/
    \item Install homebrew by running the following command on the terminal: \texttt{/bin/bash -c "\$(curl -fsSL https://raw.githubusercontent.com/Homebrew/install/HEAD/install.sh)"} (Last acessed March 11, 2022.)
    \item After installing homebrew, run \texttt{brew install hugo} on the command line.
    \item Login in GitHub Desktop by: GitHub Desktop -> Preferences -> Accounts -> Log in.
    \item After that clone the website repository: File -> Clone Repository... -> Select "\texttt{sendailogic/sendailogic.github.io}" Save the repository on any folder you like.
\end{itemize}

\section{Using GitHub Desktop}

\section{Commands for \texttt{hugo}}
\texttt{hugo} is a static site generator.
In order to update the Sendai Logic website, one only needs to write some simple files and compile the site using \texttt{hugo}.

The contents of the site are in the folder \texttt{sendailogic-hugo-source/content}.
A new post (for a seminar or event) will be a file \texttt{yyyy-mm-dd.md} on the folder \texttt{sendailogic-hugo-source/content/post}.
The simplest way to generate a file is copying an existing file and modify it.
The standard template for a post is
\begin{verbatim}
    +++
    title = "yyyy.mm.dd. speaker"
    date = yyyy-mm-dd
    description = "presentation title"
    +++
    presentation title

    <!--more-->

    - Date/Time: Month dd, yyyy (Friday) / 16:00 - 17:00

    - Speaker: Speaker (University)

    - Venue: Rm 1201, Science Complex A, Tohoku Univ.

    - Abstract: Abstract
\end{verbatim}
Note: the \texttt{date} field is the date of the creation of the file.
The date in the \texttt{title} field is the day of the presentation.
If \texttt{date} is some date in the future, the seminar page {\em will not appear on the front page}.

To edit the site, we use
\begin{verbatim}
    hugo server -s sendailogic-hugo-source
\end{verbatim}
This command is used to test the site.
This will start a server and the site will be accessible from localhost:1313/ .
If a file is modified while the server is running, the changes will be visible from the above link.

To compile the site, use
\begin{verbatim}
    hugo -s sendailogic-hugo-source -d ./..
\end{verbatim}
After editing the file, we upload the changes using \texttt{git}.



% The section for plain git is deprecated, try using something else unless you know what you are doing

% \section{Commands for \texttt{git}}
% The section for plain git is deprecated, try using something else unless you know what you are doing
% See any introduction for \texttt{git} for a complete introduction.

% To download the file for the first time use
% \begin{verbatim}
%     git pull "https://github.com/sendailogic/sendailogic.github.io.git"
% \end{verbatim}
% To update the site from the second time on, use
% \begin{verbatim}
%     git pull origin master
% \end{verbatim}
% To see the current changes on the files, use
% \begin{verbatim}
%     git status
% \end{verbatim}
% To add (or remove) new files to a commit use
% \begin{verbatim}
%     git add file.ext
% \end{verbatim}
% To add all files currently tracked that were modified use
% \begin{verbatim}
%     git add -u
% \end{verbatim}
% We use
% \begin{verbatim}
%     git commit -m "messege"
% \end{verbatim}
% bundle the changes in a commit.
% In place of \texttt{messege} write a short and clear description of the change.
% In case there are many modifications to be made it may be useful to separate the changes into multiple commits.
% At last, use
% \begin{verbatim}
%     git push origin master
% \end{verbatim}
% to upload the changes to GitHub.

% Note that to upload changes you need to be logged into GitHub.
% For instruction see https://docs.github.com/en/github/using-git/caching-your-github-credentials-in-git.
% If you are updating from a shared computer, please log out after updating the site.
% Also, use your own account to update the site and not the Sendai Logic shared account.
\end{document}